---
title: "Meta-Staggered DiD"
author: "Till Tietz"
date: "2022-10-16"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Simulating Bias

This document outlines sources of bias in estimating staggered DiD designs, 
with unbalanced panels. 

```{r pressure, echo=FALSE}
pacman::p_load(tibble,dplyr,magrittr,tidyr,ggplot2,Amelia,meta)

make_data <- function(n,
                      n_years,
                      n_groups = 5,
                      tes,
                      tes_slope,
                      unit_fes = NULL,
                      year_fes = NULL,
                      states) {
  group_splits <- levels(cut(0:1, n_groups, include.lowest = T)) %>%
    gsub("]", "", .) %>%
    gsub("\\[", "", .) %>%
    gsub("\\(", "", .) %>%
    strsplit(., ",") %>%
    lapply(., as.numeric)
  
  
  out <- tibble(unit = 1:n) %>%
    dplyr::mutate(group = runif(n()),
                  g = rep(NA, n()))
  
  if (is.null(unit_fes)) {
    out <- out %>%
      dplyr::mutate(unit_fe = rnorm(n(), 0, 0.5))
  } else {
    out <- out %>%
      dplyr::mutate(unit_fe = unit_fes)
  }
  
  r <- vector(mode = "list", n_groups)
  g_name <- paste("Group", 1:n_groups, sep = " ")
  g <- c(1:(n_groups - 1), 1000)
  
  for (i in 1:length(group_splits)) {
    r[[i]] <-
      (out$group > group_splits[[i]][1] &
         out$group <= group_splits[[i]][2])
  }
  
  for (i in 1:length(r)) {
    out$group[r[[i]]] <- g_name[i]
    out$g[r[[i]]] <- g[i]
  }
  
  out <- out %>%
    tidyr::expand_grid(year = 0:(n_years - 1))
  
  if (is.null(year_fes)) {
    out <- out %>%
      dplyr::group_by(year) %>%
      dplyr::mutate(year_fe = rnorm(length(year), 0, 1)) %>%
      dplyr::ungroup()
  } else {
    rows <- nrow(out)
    out <- out %>%
      dplyr::mutate(year_fe = rep(year_fes, rows / n_years))
  }
  
  
  out <- out %>%
    dplyr::mutate(treat = (year >= g) & (g %in% 0:(n_years - 1)),
                  error = rnorm(n(), 0, 1))
  
  te <- sapply(1:(n_groups - 1), function(i)
    paste(
      "(out$group == 'Group ",
      i,
      "') * tes[",
      i,
      "] * (out$year >= ",
      i,
      ")",
      sep = ""
    )) %>%
    paste(., collapse = " + ") %>%
    paste(
      .,
      paste(
        "(out$group == 'Group ",
        n_groups,
        "') * tes[",
        n_groups,
        "] * (out$year >= 1000)",
        sep = ""
      ),
      sep = " + "
    )
  
  te_dynamic <- sapply(1:(n_groups - 1), function(i)
    paste(
      "(out$group == 'Group ",
      i,
      "') * tes_slope[",
      i,
      "] * (out$year >= ",
      i,
      ") * (out$year - ",
      i,
      ")",
      sep = ""
    )) %>%
    paste(., collapse = " + ") %>%
    paste(
      .,
      paste(
        "(out$group == 'Group ",
        n_groups,
        "') * tes_slope[",
        n_groups,
        "] * (out$year >= 1000) * (out$year - 1000)",
        sep = ""
      ),
      sep = " + "
    )
  
  out$te <- eval(parse(text = te))
  out$te_dynamic <- eval(parse(text = te))
  
  out <- out %>%
    dplyr::mutate(y = unit_fe + year_fe + te + te_dynamic + error) %>%
    as.data.frame() %>%
    dplyr::mutate_at("treat", as.numeric) %>%
    dplyr::mutate(group_CSA = g) %>%
    dplyr::mutate(group_CSA = replace(group_CSA, group_CSA == 10000, 0)) %>%
    dplyr::mutate(treat_singular = ifelse(g == year, 1, 0))
  
  
  if (length(states) == 1) {
    state <- rep(states, n)
  } else {
    state <- sample(states, n, replace = TRUE)
  }
  
  states <- tibble(unit = 1:n,
                   state = state)
  
  out <- dplyr::left_join(out, states, by = "unit")
  
  return(out)
  
}


make_shifted <- function(n,
                     n_shifted,
                     n_years,
                     n_years_shifted,
                     n_groups,
                     n_groups_shifted,
                     tes,
                     tes_shifted,
                     tes_slope,
                     tes_slope_shifted,
                     unit_fes,
                     unit_fes_shifted,
                     year_fes,
                     year_fes_shifted,
                     states){
  
  data <- make_data(n = n,
                    n_years = n_years,
                    n_groups = n_groups,
                    tes = tes,
                    tes_slope = tes_slope,
                    unit_fes = unit_fes,
                    year_fes = year_fes,
                    states = states[1:length(states)-1])
  
  
  data_shifted <- make_data(n = n_shifted,
                            n_years = n_years_shifted,
                            n_groups = n_groups_shifted,
                            tes = tes_shifted,
                            tes_slope = tes_slope_shifted,
                            unit_fes = unit_fes_shifted,
                            year_fes = year_fes_shifted,
                            states = states[length(states)])%>%
    dplyr::mutate(unit = unit + n)
  
  data <- rbind(data,data_shifted)
  
  return(data)
}



# simulation function 

simulate <- function(n,
                     n_shifted,
                     n_years,
                     n_years_shifted,
                     n_groups,
                     n_groups_shifted,
                     tes,
                     tes_shifted,
                     tes_slope,
                     tes_slope_shifted,
                     unit_fes,
                     unit_fes_shifted,
                     year_fes,
                     year_fes_shifted,
                     states){
  
  data <- make_shifted(n = n,
                       n_shifted = n_shifted,
                       n_years = n_years,
                       n_years_shifted = n_years_shifted,
                       n_groups = n_groups,
                       n_groups_shifted = n_groups_shifted,
                       tes = tes,
                       tes_shifted = tes_shifted,
                       tes_slope = tes_slope,
                       tes_slope_shifted = tes_slope_shifted,
                       unit_fes = unit_fes,
                       unit_fes_shifted = unit_fes_shifted,
                       year_fes = year_fes,
                       year_fes_shifted = year_fes_shifted,
                       states = states)
  
  estimate <- fixest::feols(y ~ treat | unit + year, data = data)%>%
    broom::tidy()%>%
    dplyr::filter(term == "treat")%>%
    .[["estimate"]]
  
  
  true <- data%>%
    dplyr::filter(treat == 1)%>%
    dplyr::mutate(effect = te + te_dynamic)%>%
    dplyr::pull(effect)%>%
    mean()
  
  return(data.frame(tau = true, tau_hat = estimate))
}


```

We'll set up simulations with varying ammounts of treatment effect heterogeneity.
Our simulated data will have 600 units clustered into 3 groups. Two of the groups 
will have 5 identical treatment onsets. The third group will have 3 treatment onsets. 

```{r}
# homogenous
homogenous <- list(
  n = 400,
  n_shifted = 200,
  n_years = 9,
  n_years_shifted = 4,
  n_groups = 5,
  n_groups_shifted = 3,
  tes = rep(0.25, 5),
  tes_shifted = rep(0.25, 3),
  tes_slope = rep(0, 5),
  tes_slope_sifted = rep(0, 3),
  unit_fes = 0.1,
  unit_fes_shifted = 0.1,
  year_fes = rep(0.2, 9),
  year_fes_shifted = rep(0.2, 4),
  states = 1:3
)

heterogenous_years <- list(
  n = 400,
  n_shifted = 200,
  n_years = 9,
  n_years_shifted = 4,
  n_groups = 5,
  n_groups_shifted = 3,
  tes = rep(0.25, 5),
  tes_shifted = rep(0.25, 3),
  tes_slope = rep(0, 5),
  tes_slope_sifted = rep(0, 3),
  unit_fes = 0.1,
  unit_fes_shifted = 0.1,
  year_fes = (1:9 * 0.1),
  year_fes_shifted = c(0.2, 0.3, 0.4, 0.5),
  states = 1:3
)

heterogenous_units <- list(
  n = 400,
  n_shifted = 200,
  n_years = 9,
  n_years_shifted = 4,
  n_groups = 5,
  n_groups_shifted = 3,
  tes = rep(0.25, 5),
  tes_shifted = rep(0.25, 3),
  tes_slope = rep(0, 5),
  tes_slope_shifted = rep(0, 3),
  unit_fes = rnorm(400),
  unit_fes_shifted = rnorm(200),
  year_fes = (1:9 * 0.1),
  year_fes_shifted = c(0.2, 0.3, 0.4, 0.5),
  states = 1:3
)

heterogenous_full <- list(
  n = 400,
  n_shifted = 200,
  n_years = 9,
  n_years_shifted = 4,
  n_groups = 5,
  n_groups_shifted = 3,
  tes = (1:5 * 0.1),
  tes_shifted = c(0.3, 0.4, 0.5),
  tes_slope = (1:5 * 0.1),
  tes_slope_shifted = c(0.3, 0.4, 0.5),
  unit_fes = rnorm(400),
  unit_fes_shifted = rnorm(200),
  year_fes = (1:9 * 0.1),
  year_fes_shifted = c(0.2, 0.3, 0.4, 0.5),
  states = 1:3
)

sim_params <- list(homogenous,heterogenous_years,heterogenous_units,heterogenous_full)

```


```{r, echo = FALSE}
run_simulation <- function(params,n){
  
sim <- vector(mode = "list", n)

for(i in 1:length(sim)){
  
  sim[[i]] <- simulate(n = params$n,
                       n_shifted = params$n_shifted,
                       n_years = params$n_years,
                       n_years_shifted = params$n_years_shifted,
                       n_groups = params$n_groups,
                       n_groups_shifted = params$n_groups_shifted,
                       tes = params$tes,
                       tes_shifted = params$tes_shifted,
                       tes_slope = params$tes_slope,
                       tes_slope_shifted = params$tes_slope_shifted,
                       unit_fes = params$unit_fes,
                       unit_fes_shifted = params$unit_fes_shifted,
                       year_fes = params$year_fes,
                       year_fes_shifted = params$year_fes_shifted,
                       states = params$states)
  
}

sim <- dplyr::bind_rows(sim)%>%
  dplyr::mutate(diff = tau - tau_hat)

return(mean(sim$diff^2))
  
}

```

```{r}

lapply(sim_params, function(p)
  run_simulation(params = p, n = 25))%>%
  unlist()%>%
  as.data.frame()%>%
  magrittr::set_colnames("MSE")%>%
  magrittr::set_rownames(c("homogenous",
                           "heterogeneity years",
                           "heterogeneity years + units",
                           "heterogeneity tau"))%>%
  knitr::kable()

```

Pooling units with different treatment timings biases results when treatment effects vary 
substantially by treatment timing. 

### Estimation via Meta-Analysis  

We simulate heterogenous data 
```{r}

het_minor <- list(
  n = 400,
  n_shifted = 200,
  n_years = 7,
  n_years_shifted = 4,
  n_groups = 5,
  n_groups_shifted = 3,
  tes = (1:5 * 0.1),
  tes_shifted = c(0.3, 0.4, 0.5),
  tes_slope = (1:5 * 0.1),
  tes_slope_sifted = c(0.3, 0.4, 0.5),
  unit_fes = rnorm(400),
  unit_fes_shifted = rnorm(200),
  year_fes = (1:7 * 0.1),
  year_fes_shifted = c(0.2, 0.3, 0.4, 0.5),
  states = 1:3
)


het_major <- list(
  n = 400,
  n_shifted = 200,
  n_years = 7,
  n_years_shifted = 4,
  n_groups = 5,
  n_groups_shifted = 3,
  tes = (1:5 * 0.1),
  tes_shifted = c(1.3, 2.4, 3.5),
  tes_slope = (1:5 * 0.1),
  tes_slope_sifted = c(0.9, 1.2, 2.5),
  unit_fes = rnorm(400),
  unit_fes_shifted = rnorm(200),
  year_fes = (1:7 * 0.1),
  year_fes_shifted = c(0.2, 0.3, 0.4, 0.5),
  states = 1:3
)


```


```{r, echo = FALSE}

het_minor <- make_shifted(het_minor$n,
                          het_minor$n_shifted,
                          het_minor$n_years,
                          het_minor$n_years_shifted,
                          het_minor$n_groups,
                          het_minor$n_groups_shifted,
                          het_minor$tes,
                          het_minor$tes_shifted,
                          het_minor$tes_slope,
                          het_minor$tes_slope_shifted,
                          het_minor$unit_fes,
                          het_minor$units_fes_shifted,
                          het_minor$year_fes,
                          het_minor$years_fes_shifted,
                          het_minor$states)

het_major <- make_shifted(het_major$n,
                          het_major$n_shifted,
                          het_major$n_years,
                          het_major$n_years_shifted,
                          het_major$n_groups,
                          het_major$n_groups_shifted,
                          het_major$tes,
                          het_major$tes_shifted,
                          het_major$tes_slope,
                          het_major$tes_slope_shifted,
                          het_major$unit_fes,
                          het_major$units_fes_shifted,
                          het_major$year_fes,
                          het_major$years_fes_shifted,
                          het_major$states)

```


Analysis:
```{r}

estimates <- lapply(list(het_minor, het_major), function(d) {
  estimate_pooled <- fixest::feols(y ~ treat | unit + year, data = d)
  
  est <- lapply(list(c(1, 2), c(3)), function(i) {
    fixest::feols(y ~ treat |
                    unit + year, data = dplyr::filter(d, state %in% i)) %>%
      broom::tidy() %>%
      dplyr::filter(term == "treat")
  }) %>%
    dplyr::bind_rows() %>%
    dplyr::select(estimate, std.error) %>%
    magrittr::set_colnames(c("ATT", "SE")) %>%
    dplyr::mutate(model = as.character(1:2))
  
  
  estimate_meta <- meta::metagen(
    TE = est$ATT,
    seTE = est$SE,
    studlab = est$model,
    data = est,
    fixed = FALSE,
    random = TRUE,
    method.tau = "REML",
    hakn = TRUE
  )
  
  return(list(estimate_pooled, estimate_meta))
  
})


```

```{r, echo = FALSE}

dat <- list(het_minor,het_major)
het <- c("minor","major")
dshow <- vector(mode = "list", length = 2)

for(i in 1:length(estimates)) {
  
  estimate_meta <- data.frame(
    effect = "meta",
    ATT = estimates[[i]][[2]]$TE.fixed,
    SE = estimates[[i]][[2]]$seTE.fixed,
    ci.lower = estimates[[i]][[2]]$lower.fixed,
    ci.upper = estimates[[i]][[2]]$upper.fixed
  )
  
  
  estimate_pooled <- estimates[[i]][[1]] %>%
    broom::tidy() %>%
    dplyr::filter(term == "treat") %>%
    dplyr::mutate(estimation = "pooled") %>%
    dplyr::select(estimation, estimate, std.error) %>%
    dplyr::mutate(ci.lower = estimate - 1.96 * std.error,
                  ci.upper = estimate + 1.96 * std.error) %>%
    magrittr::set_colnames(c("effect", "ATT", "SE", "ci.lower", "ci.upper"))
  
  
  tau <- dat[[i]] %>%
    dplyr::filter(treat == 1) %>%
    dplyr::mutate(effect = te + te_dynamic) %>%
    dplyr::pull(effect) %>%
    mean()
  
  true <- data.frame(
    effect = "TRUE",
    ATT = tau,
    SE = NA,
    ci.lower = NA,
    ci.upper = NA
  )
  
  hetg <- data.frame(heterogeneity = rep(het[i],3))
  
  dshow[[i]] <- rbind(true,estimate_pooled,estimate_meta)%>%
    cbind(hetg,.)
  
}



dshow%>%
  dplyr::bind_rows()%>%
  knitr::kable()

```


```{r, echo = FALSE}

het_minor <- list(
  n = 400,
  n_shifted = 200,
  n_years = 7,
  n_years_shifted = 4,
  n_groups = 5,
  n_groups_shifted = 3,
  tes = (1:5 * 0.1),
  tes_shifted = c(0.3, 0.4, 0.5),
  tes_slope = (1:5 * 0.1),
  tes_slope_sifted = c(0.3, 0.4, 0.5),
  unit_fes = rnorm(400),
  unit_fes_shifted = rnorm(200),
  year_fes = (1:7 * 0.1),
  year_fes_shifted = c(0.2, 0.3, 0.4, 0.5),
  states = 1:3
)


het_major <- list(
  n = 400,
  n_shifted = 200,
  n_years = 7,
  n_years_shifted = 4,
  n_groups = 5,
  n_groups_shifted = 3,
  tes = (1:5 * 0.1),
  tes_shifted = c(1.3, 2.4, 3.5),
  tes_slope = (1:5 * 0.1),
  tes_slope_sifted = c(0.9, 1.2, 2.5),
  unit_fes = rnorm(400),
  unit_fes_shifted = rnorm(200),
  year_fes = (1:7 * 0.1),
  year_fes_shifted = c(0.2, 0.3, 0.4, 0.5),
  states = 1:3
)




run_simulation_meta <- function(runs){
  
res_major <- vector(mode = "list", length = runs)
res_minor <- vector(mode = "list", length = runs)

for(r in 1:runs){
  
  het_min <- make_shifted(
    het_minor$n,
    het_minor$n_shifted,
    het_minor$n_years,
    het_minor$n_years_shifted,
    het_minor$n_groups,
    het_minor$n_groups_shifted,
    het_minor$tes,
    het_minor$tes_shifted,
    het_minor$tes_slope,
    het_minor$tes_slope_shifted,
    het_minor$unit_fes,
    het_minor$units_fes_shifted,
    het_minor$year_fes,
    het_minor$years_fes_shifted,
    het_minor$states
  )
  
  het_maj <- make_shifted(
    het_major$n,
    het_major$n_shifted,
    het_major$n_years,
    het_major$n_years_shifted,
    het_major$n_groups,
    het_major$n_groups_shifted,
    het_major$tes,
    het_major$tes_shifted,
    het_major$tes_slope,
    het_major$tes_slope_shifted,
    het_major$unit_fes,
    het_major$units_fes_shifted,
    het_major$year_fes,
    het_major$years_fes_shifted,
    het_major$states
  )

  estimates <- lapply(list(het_min, het_maj), function(d) {
    estimate_pooled <- fixest::feols(y ~ treat | unit + year, data = d)%>%
      broom::tidy()%>%
      dplyr::filter(term == "treat")%>%
      .[["estimate"]]
    
    est <- lapply(list(c(1, 2), c(3)), function(i) {
      fixest::feols(y ~ treat |
                      unit + year, data = dplyr::filter(d, state %in% i)) %>%
        broom::tidy() %>%
        dplyr::filter(term == "treat")
    }) %>%
      dplyr::bind_rows() %>%
      dplyr::select(estimate, std.error) %>%
      magrittr::set_colnames(c("ATT", "SE")) %>%
      dplyr::mutate(model = as.character(1:2))
    
    
    estimate_meta <- meta::metagen(
      TE = est$ATT,
      seTE = est$SE,
      studlab = est$model,
      data = est,
      fixed = FALSE,
      random = TRUE,
      method.tau = "REML",
      hakn = TRUE
    )
    
    estimate_meta <- estimate_meta$TE.fixed
    
    tau <- d %>%
    dplyr::filter(treat == 1) %>%
    dplyr::mutate(effect = te + te_dynamic) %>%
    dplyr::pull(effect) %>%
    mean()
    
    
    
    return(data.frame(true = tau,
                      pooled = estimate_pooled,
                      meta = estimate_meta))
    
  })
  
  res_minor[[r]] <- estimates[[1]]
  res_major[[r]] <- estimates[[2]]
  
}

mse_minor <- res_minor%>%
  dplyr::bind_rows()%>%
  dplyr::mutate(dif_pool = (pooled - true)^2,
                dif_meta = (meta - true)^2)%>%
  dplyr::summarise(MSE_pooled = mean(dif_pool),
                   MSE_meta = mean(dif_meta))%>%
  dplyr::mutate(heterogeneity = "minor")%>%
  dplyr::select(heterogeneity,MSE_pooled,MSE_meta)

mse_major <- res_major%>%
  dplyr::bind_rows()%>%
  dplyr::mutate(dif_pool = (pooled - true)^2,
                dif_meta = (meta - true)^2)%>%
  dplyr::summarise(MSE_pooled = mean(dif_pool),
                   MSE_meta = mean(dif_meta))%>%
  dplyr::mutate(heterogeneity = "major")%>%
  dplyr::select(heterogeneity,MSE_pooled,MSE_meta)


return(rbind(mse_minor,mse_major))
  
}

```

```{r}
run_simulation_meta(runs = 20)%>%
  knitr::kable()
````
